\documentclass[10pt, letterpaper]{article}

% ---- Packages ----
\usepackage[top=0.7in, bottom=0.7in, left=0.9in, right=0.9in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}

% ---- Colors ----
\definecolor{accent}{RGB}{10, 55, 105}

% ---- Hyperref ----
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent, pdfborder={0 0 0}}

\linespread{1.04}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{9pt}

% ---- Customize per application ----
\newcommand{\company}{your organization}
\newcommand{\role}{this role}

% ============================================================
\begin{document}

% ---- Header (matches resume) ----
\begin{center}
  {\Large\bfseries Eric Forbes}\\[2pt]
  {\footnotesize\color{accent}
    5G Systems Integration Lead $\cdot$ Lockheed Martin $\cdot$ PE, PMP, PhD Candidate
  }\\[2pt]
  {\footnotesize
    \href{mailto:mr.eric.forbes@gmail.com}{mr.eric.forbes@gmail.com}
    $\;\cdot\;$
    \href{https://www.linkedin.com/in/eric--forbes}{linkedin.com/in/eric--forbes}
    $\;\cdot\;$
    Philadelphia Area, PA
  }
\end{center}

\vspace{4pt}
{\color{accent}\rule{\linewidth}{0.4pt}}

\vspace{6pt}
\today

Dear Hiring Manager,

I build teams that make products. That is the shortest honest summary of my career, and it is
what I would bring to \company{}: ownership of complex systems integration from the top down,
covering architecture, technical direction, and customers, paired with a full, hands-on
understanding of what delivery takes from the bottom up, through installation, test, and
validation.

That bottom-up understanding was earned layer by layer. I started at the test bench, certifying
consumer electronics at Intertek, then spent three years at G3 Technologies debugging cellular
protocols across four generations of wireless standards for commercial and defense customers,
down to the RF physical layer and Qualcomm chipset logs. At L3Harris I moved up the stack to own
requirements for a new Radar Warning Receiver program, engaging prime customers directly. At
Lockheed Martin that arc has continued: from defining 5G Non-Terrestrial Network architecture, to
closing the first LTE GEO satellite system, to demonstrating the world's first 5G VPX CMOSS
system with open-source software. Today, as 5G Systems Integration \& Test Lead, I am the product
owner for O-RAN and Tactical MANET deployments connecting mission-critical applications. I set
technical direction, direct sub-contractor teams across a multi-vendor environment, and travel to
integrate, test, and validate on-site with internal and external customers. When I make a
top-down architectural call, I know exactly what it costs at every layer beneath it, because I
have worked those layers myself.

I invest in long-term strategies for products, not short-term wins, and I hold myself to the same
standard. While working full time, I earned my PE license, my PMP, and a master's in wireless
communications, and I am completing a PhD in Systems Engineering at Stevens Institute of
Technology. That research is not a side pursuit; it feeds the products. Tracking 3GPP standards
working groups let me position our NTN architecture for where the standard was heading. My
published work with collaborators (five IEEE papers, including a MILCOM Poster Session Honorable
Mention) reflects how I work: as part of a team, building things that outlast a single program. I
believe deeply in team culture, because durable capabilities are delivered by teams that trust
each other, and building that trust is a leader's job.

Building is also simply what I do. Outside of work I designed, built, and continue to iterate on
an open-source RF mesh-network planning tool for Fresnel-zone analysis. It is my own product,
owned end to end, from the terrain-elevation math to the user interface.

I would welcome the chance to talk about how that combination of top-down ownership, bottom-up
technical depth, and a genuine investment in the engineers doing the work could serve \company{}.

\vspace{2pt}
Sincerely,

Eric Forbes

\end{document}
