\documentclass[9pt, letterpaper]{article}

% ---- Packages ----
\usepackage[top=0.35in, bottom=0.35in, left=0.50in, right=0.50in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% ---- Colors ----
\definecolor{accent}{RGB}{10, 55, 105}
\definecolor{tagcolor}{RGB}{35, 35, 35}

% ---- Hyperref ----
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent, pdfborder={0 0 0}}

% ---- Line spacing ----
\linespread{0.90}

% ---- Section styling ----
\titleformat{\section}
  {\small\bfseries\color{accent}}
  {}{0em}{\MakeUppercase}
  [\vspace{-4pt}\color{accent}\rule{\linewidth}{0.4pt}]
\titlespacing*{\section}{0pt}{3pt}{2pt}

% ---- List styling ----
\setlist[itemize]{leftmargin=1.1em, topsep=0pt, itemsep=0pt, parsep=0pt, label=\textbullet}
\setlist[enumerate]{leftmargin=1.8em, topsep=1pt, itemsep=0.5pt, parsep=0pt}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---- Macros ----
\newcommand{\employer}[2]{%
  \noindent{\small\textbf{#1}}\hfill{\footnotesize\textit{#2}}\par%
}
\newcommand{\subrole}[2]{%
  \noindent{\footnotesize\textit{#1}}\hfill{\footnotesize\textit{#2}}\par%
}
\newcommand{\tagline}[1]{%
  \noindent{\footnotesize\color{tagcolor}\bfseries\itshape #1}\par\vspace{1pt}%
}
\newcommand{\edu}[3]{%
  \noindent{\small\textbf{#1}}\hfill{\footnotesize\textit{#2}}\par\vspace{-2pt}%
  \noindent{\footnotesize\textit{#3}}\par%
}

% ============================================================
\begin{document}

% ---- Header ----
\begin{center}
  {\Large\bfseries Eric Forbes}\\[2pt]
  {\footnotesize\color{accent}
    5G Systems Integration Lead $\cdot$ Lockheed Martin $\cdot$ PE, PMP, PhD Candidate
  }\\[2pt]
  {\footnotesize
    \href{mailto:mr.eric.forbes@gmail.com}{mr.eric.forbes@gmail.com}
    $\;\cdot\;$
    \href{https://www.linkedin.com/in/eric--forbes}{linkedin.com/in/eric--forbes}
    $\;\cdot\;$
    Philadelphia Area, PA
  }
\end{center}

% ============================================================
\section{Profile}

\noindent{\footnotesize
Systems integration and wireless product leader grown from bench-level test engineering to
directing multi-vendor O-RAN deployments, sub-contractor teams, and on-site customer integrations
for mission-critical systems. I own delivery from the top down --- architecture through
integration, test, and validation --- with hands-on depth at every layer beneath. I build teams
that make products, investing in long-term strategy and team culture over short-term wins.
}

% ============================================================
\section{Experience}

\employer{Lockheed Martin}{May 2021 -- Present}
\subrole{5G Systems I\&T Lead, RMS}{November 2024 -- Present}
\tagline{Product owner for O-RAN and Tactical MANET deployments connecting mission-critical applications.}
\begin{itemize}
  \item Set technical direction for O-RAN software deployment on low-SWaP platforms; direct and coordinate sub-contractor teams across a multi-vendor environment.
  \item Own system architecture models through to hands-on, on-site integration and validation for internal and external customers.
\end{itemize}

\subrole{5G Systems I\&T Engineer, RMS}{April 2024 -- November 2024}
\tagline{Demonstrated the world's first 5G VPX CMOSS system with open-source software.}
\begin{itemize}
  \item Executed L2/L3 network integration, PTP timing analysis, 5G RAN/Core log debugging, and end-to-end system testing.
\end{itemize}

\subrole{4G Systems Engineer, Space}{August 2022 -- April 2024}
\tagline{Brought the first LTE GEO Satellite system to close.}
\begin{itemize}
  \item Performed full-stack eNB analysis (UE modem \& eNB); developed test plans and authored program documentation.
  \item Applied Python for large dataset analysis; Bash scripting for system debugging and automation.
\end{itemize}

\subrole{5G Systems Engineer, Space}{May 2021 -- August 2022}
\tagline{Defined architecture and requirements for 5G Non-Terrestrial Networks (NTN).}
\begin{itemize}
  \item Developed NTN requirements and network diagrams; tracked 3GPP Rel-17 NTN working groups to position the product for where the standard was heading.
\end{itemize}

\vspace{1pt}
\employer{L3Harris Technologies}{February 2020 -- May 2021}
\subrole{Sr. Specialist, Systems Engineer}{}
\tagline{Requirements Lead for a new Radar Warning Receiver (RWR) System program.}
\begin{itemize}
  \item Owned requirements development and decomposition in IBM DOORS; engaged prime customers for requirements review and program analysis.
  \item Applied MagicDraw \& SysML for MBSE across the Space and Airborne Systems division.
\end{itemize}

\vspace{1pt}
\employer{G3 Technologies, Inc.}{January 2017 -- February 2020}
\subrole{Cellular Systems Test Engineer}{}
\tagline{Protocol testing across four generations of wireless standards for commercial and defense customers.}
\begin{itemize}
  \item Debugged and tested per 3GPP/3GPP2 standards (LTE, UMTS, GSM, CDMA); analyzed Qualcomm chipsets (QXDM).
  \item Performed physical layer (RF) testing and verification; authored full system manuals and customer documentation.
\end{itemize}

\vspace{1pt}
\employer{Intertek}{January 2015 -- January 2017}
\subrole{Project Engineer}{}
\tagline{Led compliance testing and certification for consumer electronics to ANSI, CA, and IEC safety standards.}
\begin{itemize}
  \item Managed customer timelines, executed test plans, and delivered compliance reports for end-product certification.
  \item Served as Safety Officer; completed OSHA 40-hour training.
\end{itemize}

% ============================================================
\section{Education}

\edu{Stevens Institute of Technology}{2020 -- Fall 2027 (Expected)}{Doctor of Philosophy (PhD), Systems Engineering --- 5G}
\edu{Stevens Institute of Technology}{2020 -- 2024}{Graduate Certificate, Space Systems Engineering}
\edu{New Jersey Institute of Technology}{2014 -- 2016}{Master of Science (MS), Electrical Engineering --- Wireless Communications}
\edu{Penn State University}{2010 -- 2014}{Bachelor of Science (BS), Electrical Engineering}

% ============================================================
\section{Certifications}

\noindent{\footnotesize
  Project Management Professional (PMP), May 2022
  $\;\cdot\;$
  Licensed Professional Engineer (PE), New York, Dec.\ 2019 --- Electronics, Controls \& Communications
  $\;\cdot\;$
  Fundamentals of Engineering (FE), Jan.\ 2017
  $\;\cdot\;$
  IEEE Wireless Communications Professional (WCP), Oct.\ 2018
}

% ============================================================
\section{Publications}

\begin{enumerate}[label={\footnotesize[\arabic*]}, leftmargin=2em, itemsep=0pt, topsep=0pt]
  \item {\footnotesize E.~Forbes \textit{et al.}, ``Coexistent Evaluation on the Effects of Radar PRF and 5G Symbol-Based Scheduling,''
        \textit{IEEE MILCOM}, Los Angeles, CA, Oct.\ 2025. \textbf{Poster Session Honorable Mention.}}

  \item {\footnotesize E.~Forbes \textit{et al.}, ``5G and Radar Coexistence: Demonstrating Pulsed Radar Interference and 5G Performance Metrics,''
        \textit{IEEE MILCOM Demo Session}, Oct.\ 2025.}

  \item {\footnotesize E.~Forbes \textit{et al.}, ``Cellular Data-Based Indoor Localization for Smart Health Applications,''
        \textit{IEEE CHASE}, Jun.\ 2025.}

  \item {\footnotesize E.~Forbes \textit{et al.}, ``Communication Systems for Autonomous eVTOL: Regulatory Challenges, Emerging Technologies, and Future Directions,''
        \textit{IEEE}, 2025.}

  \item {\footnotesize E.~Forbes, E.~Silverstein, and Y.~Wang, ``Elevation-Aware BLER-Centric Link Adaptation for Dynamic LEO 5G NTN Systems,''
        \textit{2026 IEEE Aerospace Conference}, 2026.}
\end{enumerate}

\end{document}
